Modelling the travel time of transit vehicles in \rt through a GTFS-based road network using GPS vehicle locations

### 2019-08-10 anzjs2018/sections/05_discuss.tex
Grammar and sentence/paragraph restructuring

In this paper we described an approach to transit vehicle modelling
that enables the \rt estimation of road state from vehicle position data,
which will later be used to make arrival time predictions
that account for \rt traffic conditions.
The vehicle model, implemented using a particle filter,
allows complex bus behaviours to be modelled,
from which 
vehicle travel times along roads are estimated which are in turn used 
in the modelling of the road network state.

We have focussed on making a general framework
in which the existing models used for specific components
can easily be changed---%
for example, using a more complex model of stop dwell times
based on historical data in place of the exponential---%
or new ones added, such as implementing intersection-specific behaviour
if intersection locations are available.
Future work is planned to detect route meeting points
and use these as intersection nodes,
with the goal of further reducing road segment overlap.

@@

The results of our simulations show that the framework is a 
faesible \rt alternative.
While the timings presented were for off-peak times,
futher investigation into the choice of $N$ and $N_\text{eff}$,
as well as work removing some redudancy from the transition algorithm,
should allow us to model all vehicles during peak periods---%
when there are 2-3~times as many vehicles---%
within our 30~second timeframe target.

>>>>

In this paper, we described an approach to transit vehicle modelling
that enables the \rt estimation of road state from vehicle position data,
which will later be used to make arrival time predictions
that account for \rt traffic conditions.
The particle filter allows the modelling of complex bus behaviours,
providing estimates of vehicle travel times along roads
which are in turn used to estimate the road network state.

We have focussed on making a general framework
in which the existing models used for specific components
can easily be changed---%
for example, using a more complex model of stop dwell times
based on historical data in place of the exponential---%
or new ones added, such as implementing intersection-specific behaviour
if intersection locations are available.
Future work is planned to detect route meeting points
and use these as intersection nodes
 to further reduce road segment overlap.

@@

The results of our simulations show that the framework is a 
feasible \rt alternative.
While the timings presented were for off-peak times,
further investigation into the choice of $N$ and $N_\text{eff}$,
as well as work removing redundancy from the transition algorithm,
should allow us to model all vehicles during peak periods---%
when there are 2-3~times as many vehicles---%
within our 30-second timeframe target.
